Estimating duration in the presence of misclassification

### 2023-07-13 cis-imperfect-testing.tex
Some edits on imperfect testing

The simplest model for false negatives is by introducing a constant \emph{test sensitivity}, a probability of returning a negative test even when detectable.
Denoting the test sensitivity by $\psens$, we replace the deterministic $y_i(t)$ with a random binary variable such that:
\begin{equation}
  \prob(y_i(t) = 1) \begin{cases}
      \psens &b_i \leq t \leq e_i \\
      0 &\text{otherwise}
  \end{cases} 
\end{equation}
with $y_i(t)$ still only defined for $t \in t_i$.
However, an implausibly low value for $\psens$ is required to reproduce the rate of single positive episodes seen in CIS.
\todo[inline]{Figure demonstrating this and references to what reasonable test sensitivities are, including the estimate from the ATACCC chapter}

@@

In this section, I introduce false negatives into the model of \cref{E-perf-test:sec:model}.
We use a fairly simplified model to ensure the likelihood is tractable.
This requires modifying both $p_{ia}$ to allow for the episode possibly being longer than observed, and $p_{it}$ to allow for additional episodes being missed.

The model is only extended to model a constant test sensitivity.
Further work is required to introduce the more realistic varying test sensitivity (discussed in \cref{imperf-test:sec:discussion}).

@@

The idea when modifying $p_{ia}$ is to allow for the negative test following the last positive to be either a true or false negative.
If it is a true negative, then we have a bound on the length of the episode.
If it is a false negative, then we consider the episode's length right-censored.
The likelihood contribution for an episode is then a mixture of these two scenarios, with the mixture probability determined by the test sensitivity.

For tractability, we assume that the tests bounding the start of the infection ($l_i^{(b)}$ and $r_i^{(b)}$) are true results and hence $b_i \in [l_i^{(b)}, r_i^{(b)}]$.
Furthermore, we consider the tests only between $r_i^{(b)}$ and $l_i^{(e)}$ inclusive (the positive tests providing a lower bound on the length of the episode).
Denote these tests by $t'_i = \{ t \in t_i : r_i^{(b)} \leq t \leq l_i^{(e)} \}$ and their results by $y_i'$.
We know that the test results at times in $t_i'$ are either true positives or false negatives. 
By definition, the test at $r_i^{(e)}$ is a false negative if and only if $e_i > r_i^{(e)}$.
We proceed by considering the two cases.

@@

With false negatives, an episode with can be truncated in the following
ways:

>>>>

The simplest model for false negatives is a constant probability of returning a negative test even when detectable.
The probability of testing positive given being detectable is known as the test sensitivity.
The impact of a test sensitivity, $\psens$, less than perfect (\ie less than 100\%) is formalised by replacing the deterministic $y_i(t)$ with a random binary variable such that:
\begin{equation}
  \prob(Y_i(t) = 1) \begin{cases}
      \psens &b_i \leq t \leq e_i \\
      0 &\text{otherwise}
  \end{cases} 
\end{equation}
with $Y_i(t)$ still only defined for $t \in t_i$.
However, an implausibly low value for $\psens$ is required to reproduce the rate of single positive episodes seen in CIS.
\todo[inline]{Figure demonstrating this and references to what reasonable test sensitivities are, including the estimate from the ATACCC chapter}

@@

In this section, I introduce a simple model of false negatives into the model of \cref{E-perf-test:sec:model}.
The simple model ensures the likelihood remains tractable.
This requires modifying both $p_{ia}$ to allow for the episode possibly being longer than observed, and $p_{it}$ to allow for additional episodes being missed.

A constant test sensitivity is assumed throughout this section.
Further work is required to introduce the more realistic varying test sensitivity (discussed in \cref{imperf-test:sec:discussion}).

@@

I modify $p_{ia}$ to allow the negative test following the last positive to be a false negative.
If it is a false negative, then we consider the episode's length right-censored.
However, if it is in fact a true negative, then we are in the same case as before with a bound on the length of the episode.
A mixture of these scenarios then forms the episode's likelihood contribution, with the mixture probability determined by the test sensitivity.

For tractability, assume that the negative test bounding the start of the infection, at $l_i^{(b)}$, is a true negative.
This assumption is reasonable because the test sensitivity is high early in an infection, therefore $l_i^{(b)}$ is unlikely to be a false negative.
\todo{Are these bounds correct?}
We will consider only the tests between $r_i^{(b)}$ and $l_i^{(e)}$ inclusive (the positive tests providing a lower bound on the length of the episode).
Denote these tests by $t'_i = \{ t \in t_i : r_i^{(b)} \leq t \leq l_i^{(e)} \}$ and their results by $y_i'$.
We know that the test results at times in $t_i'$ are either true positives or false negatives. 
By definition, the test at $r_i^{(e)}$ is a false negative if and only if $e_i > r_i^{(e)}$.
We proceed by considering the two cases.

@@

With false negatives, an episode with can be undetected in the following
ways:
